---
title: "R Markdown "
author: "Dr Josh A Hodge"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(dplyr)
require(tidyr)
require(stringr)
require(ggplot2)
```

# Background

RMarkdown is a dynamic document that enables you to develop code and embed it inline in a word file. RMarkdowns are used a lot for reproducible research. You will be required to submit a RMarkdown for your coursework (MSc's only) as part of the Biological Computing module.

# Writing with Markdown

Headings in an RMarkdown are indicated by using hastags. In the RMarkdown document increasing the number of hashtags will decrease the size of the heading, for example:

# Example of one hastag

###### Example of six hastags

You can also **bold** your text, *italicise*, ^superscript^ and ~subscript~.

Other useful things are of course creating number lists like:

1.  Number one

2.  Number two

Or bullet pointing:

-   bullet one

# Inline Coding, Table and Figures 

The best feature of RMarkdown is the fact you can include code embedded in your documents, for example:

```{r}
data("iris") #loading iris dataset 
```

You can include tables of your data:

```{r}
knitr::kable(head(iris),caption = "First Five Rows of Iris")
```

And you can create tables without having the code in your document using `echo=FALSE` in the curly brackets of `{r, echo=FALSE}`.

```{r, echo=FALSE}
knitr::kable(head(iris),caption = "First Five Rows of Iris")
```

With creating figures, you can customised a lot in the ```{r}```, such as: 

- Figure alignment: ```{r, fig.align="center"}```, ```{r, fig.align="left"}``` or ```{r, fig.align="right"}``` 

- Figure caption or legend: ```{r, fig.cap="legend"}```

- Figure dimensions: ```{r, fig.width=inches}``` and/or ```{r, fig.height=inches}```

- Figure resolution: ```{r, dpi=}``` where a higher value of dpi means higher resolution: try 300, 500 or 700. 

So let's make a figure using: ```{r, fig.align="center", fig.cap="Figure-1: relationship between petal length (cm) and sepal length (cm)", dpi=500}```

```{r, fig.align="center", fig.cap="Figure-1: relationship between petal length (cm) and sepal length (cm)", dpi=500}
plot(iris$Petal.Length~iris$Sepal.Length, xlab="Sepal Length (cm)", ylab="Petal Length (cm)")
```
